Cover Times of Random Walks

### 2019-05-09 paper.tex
minor
minor edits
some of Bill's edits

Next consider a particular case of coupon collecting called the birthday problem.
How many people would we need to ensure that every day of the year
(excluding February 29) is represented as a birthday?
A lower bound is certainly 365 but there is no upper bound.

@@

\subsection{Definitions}
We consider an undirected, connected graph $G$ without multi-edges.
Let $V(G)$ be the set of vertices and let $E(G)$ be the set of edges on $G$.
Then $n$ is the number of vertices $|V(G)|$.
We say $i\sim j$ for $i$ and $j$ in the vertex set $V(G)$ if $(i,j)$ is in $E(G)$.
Assume that each vertex is accessible from every other vertex.
That is, there is a set of edges connecting any $x$ to any $y$.

Let $C_{i,j}=C_{j,i}$ be the non-negative weight of the edge between vertices $i$ and $j$.
We will mostly consider unweighted graphs
such that $C_{i,j} = 1$ if $i \sim j$ and $C_{i,j} = 0$ otherwise.

Define the weight of vertex $i$ 
\begin{align}
C_i &= \sum_{j:i \sim j} C_{i,j}. \nonumber
\end{align}
In the unweighted case, $C_i$ is the degree of vertex $i$.

@@

Let $T_{j}$ be the number of steps until the first visit to $j$.
Formally,
\begin{align}
T_{j} &= \textrm{min} \left\{t > 0 : X_t = j \right\}. \nonumber
\end{align}
Let the hitting time $\hit$ be the maximum expected time between two vertices on $G$.
Note that $\E_i[T_j] = \E[T_j | X_0 = i]$.
Formally, 
\begin{align}
\hit &= \max_{i,j \in V(G)} \E_i[T_j]. \nonumber
\end{align}
Let the cover time variable $\cov$ be the first time all vertices have been
visited by the random walk $(X_t)$.
Formally, $\cov$ is the minimum time that for all $i \in V(G)$
there exists $t \leq \cov$ such that $X_t = i$.
We define the cover time as the expected value of $\cov$ from
the worst initial vertex.
Formally,
\begin{align}
\tcov &= \max_{j \in V(G)} \E_j[\cov] . \nonumber
\end{align}

@@

We begin in \cref{sec:small_example}.
(\cref{sec:structured_graphs} primarily relies on \cite{BH94}.)
We see that it is always possible to exactly calculate the cover time
of graph but it is in general very difficult to do so.
For the remainder of this section, we investigate
structured graphs that are exceptions to the rule:
the complete graph, line graphs, and simple cycles.

@@

We write the cover time in terms of $X_i$ and use linearity of expectation.
\begin{align}
\tcov&= \E[X_1+X_2+X_3+\cdots+X_{n-1}] = \sum_{i=1}^{n-1} \E[X_i] \nonumber
\end{align}

@@

\begin{comment}
It follows that $X_i$ is geometric with distribution
\begin{align}
\pr(X_i = k) = (1-p_i)^{k-1}p_i, \nonumber
\end{align}
where $p_i$ is the probability of moving to a previously unvisited vertex.
\end{comment}
We now find the probability $p_i$ that 
we go to a previously unvisited vertex is $(n-i)/(n-1)$.
This is because there are $n-i$ unvisited vertices and a total of $n-1$ adjacent vertices.
It follows that $\E[X_i] = (n-1)/(n-i)$.
Then
\begin{align}
\tcov&=   \sum_{i=1}^{n-1} \frac{n-1}{n-i} \nonumber \\
&=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+\cdots+1\right). \nonumber
\end{align}

@@

Let $\{a, a+1, \ldots, b-1, b\}$ 
denote the set of vertices we have visited.
Since the walk is on a line, we can $[a,b]$ for the range
of the walk where $a$ is the smallest 
and $b$ is the largest vertex we have visited.
Notice that if $a \leq -n$ or $b \geq n$, we have covered all $n$ vertices
on the simple cycle and conclude the random walk.

In a slight abuse of notation, let $T_k$ be the 
number of steps until we reach $k$ distinct vertices.
Formally, $T_k = \min\{t: b-a+1 = k\}$.
Then by telescoping,
\begin{align}
\tcov &= \E[T_n] = \E[(T_2 - T_1) + (T_3 - T_2) + \cdots + 
(T_k - T_{k-1}) + \cdots + (T_n - T_{n-1})] \nonumber
\end{align}

@@

Recall that $\pi_a$ is the probability that $(X_t) = a$.
By a similar argument, $1/\pi_a$ is the expected return time to $a$.

Thus the expected time from $a$ to $b$ and back is
the expected number of returns to $a$ before we reach $b$ times
the expected number of steps for each return to $a$.
The commute time identity follows
\begin{align}
E_a[T_b] + E_b[T_a] = \frac{1}{\pi_a}\frac{1}{\pr_a(T_b < T_a)} = \Reff C.
\label{eqn:commute}
\end{align}

@@

We use \cref{eqn:dist} to calculate the probability
that all birthdays are represented in populations of 
size $r=2190$ and $r=1825$, respectively.
The number of vertices $n$ is 365 so $n\log n = 2153$.
It follows that
\begin{align}
\pr(\cov \leq 2190) &= \pr \left(\frac{\cov - 2153}{365} \leq
\frac{37}{365}\right) \nonumber \\
&\approx e^{-e^{-.10137}} \approx 0.40511 \nonumber
\end{align}
but 
\begin{align}
\pr(\cov \leq 1825) &= \pr \left(\frac{\cov - 2153}{365} \leq
\frac{328}{365}\right) \nonumber \\
&\approx e^{-e^{-.8.9863}} \approx 0.08576. \nonumber
\end{align}

>>>>

Next consider a particular case of coupon collecting called the birthday problem.
Assuming all 365 days of the year, excluding February 29, are equally likely,
how many people would we need to ensure each birthday is represented
by at least one person?
A lower bound is certainly 365 but it is possible to get an arbitrarily
large population without covering each birthday.

@@

\subsection{Definitions}
We consider an undirected, connected graph $G$ without multi-edges.
Let $V(G)$ be the set of vertices and let $E(G)$ be the set of edges on $G$.
Then $n$ is the number of vertices $|V(G)|$.
We say $i\sim j$ for $i$ and $j$ in the vertex set $V(G)$ if $(i,j)$ 
is in $E(G)$.
Assume that each vertex is accessible from every other vertex.
That is, for $x$ and $y$ there exists a path
$x=v_0 \sim v_1 \sim \cdots \sim v_n = y$.

Let $C_{i,j}=C_{j,i}$ be a non-negative weight assinged to the edge
between vertices $i$ and $j$.
We will mostly consider unweighted graphs,
meaning $C_{i,j} = 1$ if $i \sim j$ and $C_{i,j} = 0$ otherwise.

Define the weight of vertex $i$ 
\begin{align}
C_i &= \sum_{j:i \sim j} C_{i,j}. \nonumber
\end{align}
In the unweighted case, $C_i$ is simply the degree of vertex $i$.

@@

Let $T_{j}$ be the number of steps until the first visit to $j$
after time time $t=0$.
Formally,
\begin{align}
T_{j} &= \textrm{min} \left\{t > 0 : X_t = j \right\}. \nonumber
\end{align}
Let $\E_i[T_j] = \E[T_j | X_0 = i]$.
This is the expected time of the first visit to $j$ given
that the random walk started in vertex $i$.
Then $\E_j[T_j]$ is the return time to $j$.
Now define the hitting time $\hit$ for the graph
be the maximum expected time between two vertices on $G$.

Formally, 
\begin{align}
\hit &= \max_{i,j \in V(G)} \E_i[T_j]. \nonumber
\end{align}
Let the cover time variable $\cov$ be the first time all vertices have been
visited by the random walk $(X_t)$.
Formally, $\cov$ is the minimum time that for all $i \in V(G)$
there exists $t \leq \cov$ such that $X_t = i$.
We define the cover time as the expected value of $\cov$ from
the worst initial vertex.
Formally,
\begin{align}
\tcov &= \max_{j \in V(G)} \E_j[\cov] . \nonumber
\end{align}

@@

We begin in \cref{sec:small_example}.
(\cref{sec:structured_graphs} primarily relies on \cite{BH94}.)
We see that while in principle it is always possible to exactly 
calculate the cover time
of graph, it is in general very difficult to do so.
For the remainder of this section, we investigate
structured graphs for which exact cover time analysis is tractable:
the complete graph, line graphs, and simple cycles.

@@

We write the cover time in terms of $X_i$ and use linearity of expectation.
\begin{align}
\tcov&= \E[X_1+X_2+X_3+\cdots+X_{n}] = \sum_{i=1}^{n} \E[X_i] \nonumber
\end{align}

@@

\begin{comment}
It follows that $X_i$ is geometric with distribution
\begin{align}
\pr(X_i = k) = (1-p_i)^{k-1}p_i, \nonumber
\end{align}
where $p_i$ is the probability of moving to a previously unvisited vertex.
\end{comment}
We now find the probability $p_i$ that 
we go to a previously unvisited vertex is $(n-i+1)/(n-1)$.
This is because there are $n-i+1$ unvisited 
vertices and a total of $n-1$ adjacent vertices.
It follows that $\E[X_i] = (n-1)/(n-i+1)$.
Then
\begin{align}
\tcov&=   \sum_{i=1}^{n} \frac{n-1}{n-i+1} \nonumber \\
&=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+\cdots+1\right). \nonumber
\end{align}

@@

Let $\{a, a+1, \ldots, b-1, b\}$ 
denote the set of vertices we have visited.
Since the walk is on a line, we can write $[a,b]$ for the range
of the walk where $a$ is the smallest 
and $b$ is the largest vertex we have visited.
Notice that if $a \leq -n$ or $b \geq n$, we have covered all $n$ vertices
on the simple cycle and conclude the random walk.

In a slight abuse of notation, let $T_k$ be the 
number of steps until we reach $k$ distinct vertices.
Formally, $T_k = \min\{t: b-a+1 = k\}$.
Then by telescoping,
\begin{align}
\tcov &= \E_0[T_n] = \E[(T_2 - T_1) + (T_3 - T_2) + \cdots + 
(T_k - T_{k-1}) + \cdots + (T_n - T_{n-1})] \nonumber
\end{align}

@@

Recall that $\pi_a$ is the probability that $(X_t) = a$.
By a similar argument, $1/\pi_a$ is the expected return time to $a$.
If we condition on reaching $b$ before turning to $a$,
\begin{align}
\frac{1}{\pi_a} &= \E_a[T_a] =
\E_a[T_a|T_b < T_a] \pr(T_b<T_a) +
\E_a[T_a|T_a < T_b] \pr(T_a<T_b) \nonumber.
\end{align}

Considering the cases that we either reach $b$ or not before
returning to $a$,
\begin{align}
\E_a[T_b] + \E_b[T_a] &= 
\E_a[T_a | T_b < T_a] + 
\E_a[T_a | T_a < T_b] (\frac{1}{\pr(T_b<T_a)} - 1) \nonumber.
\end{align}
Observe that $1/\pr(T_b<T_a)-1 = (1-\pr(T_b<T_a))/\pr(T_b<T_a)$, 
which simplifies to $\pr(T_a<T_b)/\pr(T_b<T_a)$.
Multiplying by the probability we reach $b$ before returning to $a$,
\begin{align}
\E_a[T_a|T_b < T_a] \pr(T_b<T_a) + \E_a[T_a|T_a<T_b] \pr(T_a<T_b)=\frac{1}{\pi_a} \nonumber
\end{align}
and the commute identity follows
\begin{align}
E_a[T_b] + E_b[T_a] = \frac{1}{\pi_a}\frac{1}{\pr_a(T_b < T_a)} = \Reff C.
\label{eqn:commute}
\end{align}

@@

We use \cref{eqn:dist} to calculate the probability
that all birthdays are represented in populations of 
size $r=2190$ and $r=1825$, respectively.
The number of vertices $n$ is 365 so $n\log n = 2153$.
It follows that
\begin{align}
\pr(\cov \leq 2190) &= \pr \left(\frac{\cov - 2153}{365} \leq
\frac{37}{365}\right) \nonumber \\
&\approx e^{-e^{-0.10137}} \approx 0.40511 \nonumber
\end{align}
but 
\begin{align}
\pr(\cov \leq 1825) &= \pr \left(\frac{\cov - 2153}{365} \leq
\frac{-328}{365}\right) \nonumber \\
&\approx e^{-e^{-0.89863}} \approx 0.08576. \nonumber
\end{align}

### 2019-05-09 talk.tex
minor edits
some of Bill's edits

\DeclareMathOperator{\E}{\textrm{E}}		     % expected value
\DeclareMathOperator{\pr}{\mathrm{P}}		     % probability

\title{Cover Times of Random Walks}
\author{R. Teal Witter}
\date{May 9, 2019}

@@

		\node (m) at (-1.2,1.75) {
			\begin{tikzpicture}[scale = 3]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
%			    \node (l) at (.5, 1.1) {$t_{cov}$};
			    \node (bl) at (0,0) {};
			    \node[current] (tl) at (0,1) {};
			    \node (br) at (1,0) {};
			    \node (tr) at (1,1) {};;
			\end{tikzpicture}
		};
		\pause

@@

\begin{frame}{A Small Graph}
\small
\begin{align}
\E[t_{cov}] &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{b} 
\only<2->{= \frac{43}{6}}\nonumber \\
\textrm{a} &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{c} \nonumber \\
\textrm{b} &= 1 + \frac{1}{2}\textrm{b} + \frac{1}{2}\textrm{e} \nonumber \\
\textrm{c} &= 1 + 1\textrm{e} \nonumber \\
\textrm{d} &= 1 + \frac{1}{3}\textrm{a} + \frac{1}{3}\textrm{e} + \frac{1}{3}\textrm{f} \nonumber \\
\textrm{e} &= 1 + \frac{1}{3}\textrm{c} + \frac{1}{3}\textrm{e} + \frac{1}{3} 0\nonumber \\
\textrm{f} &= 1 + \frac{1}{2}\textrm{g} + \frac{1}{2} 0 \nonumber \\
\textrm{g} &= 1 + \frac{2}{3}\textrm{f} + \frac{1}{3} 0\nonumber
\end{align}
\end{frame}

@@

\begin{frame}{Complete Graph with Self-edges}
Let $X_i$ be the number of steps from $i-1$ to $i$ distinct vertices.
\only<2-> {
\begin{align}
\E[t_{cov}] &= \E[X_1+X_2+X_3+\cdots+X_{n}] \nonumber
\end{align}
}

\only<3-> {$X_i \sim \textrm{Geom}(\frac{n-i+1}{n})$}
\only<4-> {so $\E[X_i] = \frac{n}{n-i+1}$}
\only<5-> {and
\begin{align}
\E[t_{cov}] &= n\left(\frac{1}{n}+\frac{1}{n-1}+\cdots+1\right) \nonumber
\end{align}
}
\end{frame}

@@

\begin{frame}{Matthews Method}
\begin{theorem}
Consider a random walk on an arbitrary connected graph with $n$ vertices. Then
\end{theorem}
\begin{align}
\E[t_{cov}] &\leq t_{hit} \left(1 + \frac{1}{2} + \frac{1}{3} + \cdots + \frac{1}{n-1} \right). \nonumber
\end{align}
\end{frame}

@@

Let $T_k$ be the first time vertices 
$\sigma_1, \sigma_2, \ldots, \sigma_k$ have all been visited.
\pause
\begin{align}
\E[t_{cov}] &\leq \E_n[{T_{n-1}}]  \nonumber \\
&= \E_n[T_1 + (T_2 - T_1) + \cdots + (T_{n-1} - T_{n-2})] . \nonumber
\end{align}

@@

\begin{frame}{Poisson Distribution}
After $r$ steps of a random walk, let $A_i$ be the probability that
vertex $i$ is unvisited.
\begin{align}
\pr(A_i) = (1-1/n)^r \nonumber
\end{align}
\pause
Let $N_n$ be the number of unvisited vertices.
\begin{align}
\E[N_n] &= n(1-1/n)^r. \nonumber  \\
&=n[(1-1/n)^n]^{r/n} = n e^{r/n} \nonumber
\end{align}
\pause
I promise that 
\begin{align}
N_n/n &\xrightarrow{p} \E[N_n/n] \nonumber
\end{align}

@@

\begin{frame}{Poisson Distribution}
\begin{align}
r &= n \log n + nx \nonumber \\
N_n &= ne^{-r/n} = ne^{-\log n - x} = n n^{-1} e^{-x} \rightarrow  e^{-x} \nonumber
\end{align}
\begin{theorem}
If $ne^{-r/n} \rightarrow \lambda \in [0, \infty)$, then the number of unvisited
vertices approaches a Poisson distribution with mean $\lambda$.
\end{theorem}
\pause
\begin{align}
\pr(N_n=0) = \pr(t_{cov} \leq r) &\rightarrow e^{-e^{-x}} \nonumber \\
\pr(t_{cov} - n \log n\leq nx) &\rightarrow e^{-e^{-x}} \nonumber
\end{align}
\end{frame}

\begin{frame}{Birthday Problem}
What is the probability all birthdays are covered in a town of 1825?
How about a town of 2190?
\pause
\begin{align}
\pr(t_{cov} \leq 1825) &= \pr \left(\frac{t_{cov} - 2153}{365} \leq
\frac{328}{365}\right) \nonumber \\
&\approx e^{-e^{-0.89863}} \approx 0.08576. \nonumber
\only<3->{
\\\pr(t_{cov} \leq 2190) &= \pr \left(\frac{t_{cov} - 2153}{365} \leq
\frac{37}{365}\right) \nonumber \\
&\approx e^{-e^{-0.10137}} \approx 0.40511 \nonumber
}
\end{align}

@@

\begin{frame}{Birthday Problem}
\begin{tikzpicture}[scale=.37]
\node (graph) at (0,0) {\includegraphics[scale=.1, height=7cm]{birthdays}};
\node (title) at (1, 10) {Cover Times of the Birthday Problem (1000 trials)};
\node[rotate=90] (ylabel) at (-13,2) {$\pr(t_{cov} \leq r)$};
\node (xlabel) at (0,-9) {$r$};
\end{tikzpicture}
\end{frame}

>>>>

\DeclareMathOperator{\E}{\textrm{E}}		     % expected value
\DeclareMathOperator{\pr}{\mathrm{P}}		     % probability 
\DeclareMathOperator{\cov}{t_{cov}}	             % cover time

\title{Cover Times of Random Walks}
\author{R. Teal Witter}
\institute{Middlebury College}
\date{May 9, 2019}

@@

		\node (m) at (-1.2,1.75) {
			\begin{tikzpicture}[scale = 3]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
%			    \node (l) at (.5, 1.1) {$\cov$};
			    \node (bl) at (0,0) {};
			    \node[current] (tl) at (0,1) {};
			    \node (br) at (1,0) {};
			    \node (tr) at (1,1) {};;
			\end{tikzpicture}
		};
		\pause

@@

\begin{frame}{A Small Graph}
\small
\begin{align}
\E[\cov] &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{b} 
\only<2->{= \frac{43}{6}}\nonumber \\
\textrm{a} &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{c} \nonumber \\
\textrm{b} &= 1 + \frac{1}{2}\textrm{b} + \frac{1}{2}\textrm{e} \nonumber \\
\textrm{c} &= 1 + 1\textrm{e} \nonumber \\
\textrm{d} &= 1 + \frac{1}{3}\textrm{a} + \frac{1}{3}\textrm{e} + \frac{1}{3}\textrm{f} \nonumber \\
\textrm{e} &= 1 + \frac{1}{3}\textrm{c} + \frac{1}{3}\textrm{e} + \frac{1}{3} 0\nonumber \\
\textrm{f} &= 1 + \frac{1}{2}\textrm{g} + \frac{1}{2} 0 \nonumber \\
\textrm{g} &= 1 + \frac{2}{3}\textrm{f} + \frac{1}{3} 0\nonumber
\end{align}
\end{frame}

@@

\begin{frame}{Complete Graph with Self-edges}
Let $X_i$ be the number of steps from $i-1$ to $i$ distinct vertices.
\only<2-> {
\begin{align}
\E[\cov] &= \E[X_1+X_2+X_3+\cdots+X_{n}] \nonumber
\end{align}
}

\only<3-> {$X_i \sim \textrm{Geom}(\frac{n-i+1}{n})$}
\only<4-> {so $\E[X_i] = \frac{n}{n-i+1}$}
\only<5-> {and
\begin{align}
\E[\cov] &= n\left(\frac{1}{n}+\frac{1}{n-1}+\cdots+1\right) \nonumber
\end{align}
}
\end{frame}

@@

\begin{frame}{Matthews Method}
\begin{theorem}
Consider a random walk on an arbitrary connected graph with $n$ vertices. Then
\end{theorem}
\begin{align}
\E[\cov] &\leq t_{hit} \left(1 + \frac{1}{2} + \frac{1}{3} + \cdots + \frac{1}{n-1} \right). \nonumber
\end{align}
\end{frame}

@@

Let $T_k$ be the first time vertices 
$\sigma_1, \sigma_2, \ldots, \sigma_k$ have all been visited.
\pause
\begin{align}
\E[\cov] &\leq \E_n[{T_{n-1}}]  \nonumber \\
&\leq \E_n[T_1 + (T_2 - T_1) + \cdots + (T_{n-1} - T_{n-2})] . \nonumber
\end{align}

@@

\begin{frame}{Cover Time Distribution}
After $r$ steps of a random walk, let $A_i$ be the event that
vertex $i$ is unvisited.
\begin{align}
\pr(A_i) = \pr(\textrm{not visited in one step})^r = (1-1/n)^r \nonumber
\end{align}
\pause
Let $N_n$ be the number of unvisited vertices.
\begin{align}
\E[N_n] &= \sum_{i=1}^n \pr(A_i) = n(1-1/n)^r \nonumber  \\
&=n[(1-1/n)^n]^{r/n} \sim n e^{-r/n} \nonumber
\end{align}

@@

\begin{frame}{Cover Time Distribution}
Introduce $x$ and set $r = n \log n + nx$.
\begin{align}
N_n &\sim ne^{-r/n} = ne^{-\log n - x} = n n^{-1} e^{-x} \rightarrow  e^{-x} \nonumber
\end{align}
\begin{theorem}
If $ne^{-r/n} \rightarrow \lambda \in [0, \infty)$, then the number of unvisited
vertices approaches a Poisson distribution with mean $\lambda$.
\end{theorem}
\pause
\begin{align}
\pr(N_n=0) = \pr(\cov \leq r)
= \pr(\cov - n \log n\leq nx)
\rightarrow e^{-e^{-x}} \nonumber
\end{align}
\end{frame}

\begin{frame}{Birthday Problem}
What is the probability all birthdays are covered in a town of 1825?
How about a town of 2190?
\pause
\begin{align}
\pr(\cov \leq 1825) &= \pr \left(\frac{\cov - 2153}{365} \leq
\frac{-328}{365}\right) \nonumber \\
&\approx e^{-e^{-0.89863}} \approx 0.08576 \nonumber
\only<3->{
\\\pr(\cov \leq 2190) &= \pr \left(\frac{\cov - 2153}{365} \leq
\frac{37}{365}\right) \nonumber \\
&\approx e^{-e^{-0.10137}} \approx 0.40511 \nonumber
}
\end{align}

@@

\begin{frame}{Birthday Problem}
\begin{tikzpicture}[scale=.37]
\node (graph) at (0,0) {\includegraphics[scale=.1, height=7cm]{birthdays}};
\node (title) at (1, 10) {Cover Times of the Birthday Problem (1000 trials)};
\node[rotate=90] (ylabel) at (-13,2) {$\pr(\cov \leq r)$};
\node (xlabel) at (0,-9) {$r$};
\end{tikzpicture}
\end{frame}
